Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-03 paper/paper.tex
hscc17
Signed-off-by: Alessandro Abate <aabate@Alessandros-MacBook-Pro.local>

@@

\title{Counterexample-guided Synthesis \\
of Closed-loop Digital Control Systems}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

@@

\noindent where $\sigma_{Q}^{2}$ is the variance of quantization noise and
$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
the signal from the digital controller), which is provided to the plant by
means of ZOH.
%
\begin{proof}
%
Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can
be represented by the following pulse transfer function (without
quantization noise effect):
%
\begin{equation}
\label{eq:tfwithout}
G(z)=\frac{Y(z)}{U(z)}=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M}}{1+a_{1}z^{-1}+a_{2}z^{-2}+\cdots+a_{N}z^{-N}},
\end{equation}
%
\noindent where $Y(z)$ is the z-transform of the plant output signal without
noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is
provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer
function numerator and denominator, respectively.

>>>>

\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\red}[1]{{\color{red}#1}}

@@

\title{
Sound and Automated Synthesis of Digital Controllers for Physical Plants 
%Counterexample-guided Synthesis of Closed-loop Digital Control Systems
}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

\blue{Please insert a figure clearly distinguishing between continuous and discretised/quantised plant - a template is in a picture sent out by Lucas late last week. 
We should have 
\begin{itemize}
\item 
$G(s) = \frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties 
\item 
$G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients 
\item

\end{itemize}
}

@@

\noindent where $\sigma_{Q}^{2}$ is the variance of quantization noise and
$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
the signal from the digital controller), which is provided to the plant by
means of ZOH.

\red{[Please write out a formal statement for the proof below:]}
%
\begin{proof}
%
Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can
be represented by the following pulse transfer function (without
quantization noise effect):
%
\begin{equation}
\label{eq:tfwithout}
G(z)=\frac{Y(z)}{U(z)}=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M}}{1+a_{1}z^{-1}+a_{2}z^{-2}+\cdots+a_{N}z^{-N}},
\end{equation}
%
\noindent where $Y(z)$ is the z-transform of the plant output signal without
noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is
provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer
function numerator and denominator, respectively.
